```
\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}

\hypersetup{breaklinks=true,%
pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}

\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document% Header Section
\begin{resume_header}
\name{Anand Mishra}
\program{Btech IIT Varanasi - Computer Science and Engineering}
\contact{anand.mishra.off@gmail.com \hspace{2cm} +91 8825317943 \hspace{2cm} Jharkhand, India}
\end{resume_header}

% Education Section
\begin{resume_section}{Education}          

  \begin{resume_subsection}[Varanasi, 2020-2024]{Indian Institute of Technology}
    \begin{subitems}
      \item Btech Engineering majoring in Computer Science and Engineering.
      \item CPA: 9/10
    \end{subitems}
  \end{resume_subsection}
  
  \begin{resume_subsection}[SAIL Township Ranchi, Jharkhand 2017-2019]{Delhi Public School School}
    \begin{subitems}
      \item Cumulative Average: 92\%
     \end{subitems}
  \end{resume_subsection}

\end{resume_section}

% Skills Section
\begin{resume_section}{Skills}
  \begin{nospacetabbing}
    \textbf{Technical Skills:}  \= C/C++, Python, Git\\*
    \textbf{Interests:} \>Problem solving, Competitive programming\\*
  \end{nospacetabbing}
\end{resume_section}

% Experience Section
\begin{resume_section}{Experience}

  % D. E. Shaw India section with projects
  \begin{resume_subsection}[Jun 2024 to present]{D E Shaw India}
    % Project 1
    \begin{resume_subsection}{Automated Data Pipeline to send report}
      \begin{subitems}

      
        \item Designed and implemented an automated \textbf{ETL pipeline} to generate and distribute quarterly reports to analysts, reducing manual effort and ensuring timely data delivery.
        \item Implemented error handling and logging mechanisms to improve pipeline reliability and maintainability.
        \item Exposure: Python, Redshift, AWS S3
      \end{subitems}
    \end{resume_subsection}

    % Project 2
    \begin{resume_subsection}{Optimized ETL pipeline}
      \begin{subitems}
        \item Enhanced the data enrichment process by optimizing SQL queries in Amazon Redshift, {\textbf{reducing processing time by 30\%}}.
\item           Utilized Redshift’s internal query mechanisms (distribution keys, sort keys, query pruning) to improve efficiency.
\item Refactored complex SQL transformations to minimize data shuffling and optimize resource utilization.
\item Technologies: Python, SQLAlchemy, AWS S3, Amazon Redshift
      \end{subitems}
    \end{resume_subsection}

  \end{resume_subsection}
\end{resume_section}

% Projects/Internship Programs Section
\begin{resume_section}{Projects/Internship Programs}

  \begin{resume_employer}{D E Shaw summer internship program}{Under Mr. Ganesh Kumar}{May 2023 to July 2023}{Hyderabad}
  
    \item Developed an ETL pipeline to extract data from Wikidata and create/update a temporal knowledge graph.
    \item Exposure: Python, SPARQL, Neo4j, Cypher
  \end{resume_employer}

    \begin{resume_employer}{Microsoft engage mentorship program}{Under Mr. Vijay Bandi}{Jan 2022 to Apr 2022}{Varanasi}
    \item Implemented Movie recommendation system using KNN and bag of words.
    \item Exposure: Python, KNN, Cosine similarity, Streamlit, Bag of Words
  \end{resume_employer}

    \begin{resume_employer}{LLM-Powered Chatbot for QnA}{Self}{}{Hyderabad}
    \item Fine-tuned an open-source LLM (Mistral/TinyLlama) on a domain-specific        dataset.
    \item Optimized hyperparameters using LoRA for efficient performance.
    \item Deployed a chat interface with Flask/FastAPI.
    \item Exposure: Python, PyTorch, Hugging Face, LoRA, FastAPI.
  \end{resume_employer}

  \begin{resume_employer}{Document Search with RAG}{Self}{}{Hyderabad}
    \item Implemented retrieval-augmented generation (RAG) using FAISS and LangChain.
    \item Optimized hyperparameters using LoRA for efficient performance.
    \item Enabled efficient semantic search over large document collections.
    \item Used OpenAI/LLamaIndex for response generation.
    \item Exposure: 
Python, FAISS, LangChain, OpenAI API.
  \end{resume_employer}

  \begin{resume_employer}{Stock market predictor}{Under Prof. Pratik Chattopadhyay}{Aug 2022 to Nov 2022}{Varanasi}
    \item Predicted stock prices using historical data and LSTM (Long Short Term Memory).
    \item Exposure: Pandas, Numpy, LSTM
  \end{resume_employer}


\end{resume_section}

% Other Achievements Section
\begin{resume_section}{Other Achievements}
  \begin{itemize}
    \item Rank 1337 in JEE Advanced 2020.
    \item Global rank 344 at IMC PROSPERITY Trading Challenge.
    \item Specialist in Codeforces | max rating: 1556.
    \item Global rank 225 at March Cook-Off 2022 Div 2.
    \item Global rank 926 at Codeforces Round 782 Div 2.
    \item Qualified NSO 2017 for the 2nd round.
    \item Part of Microsoft engage mentorship program under Mr. Vijay Bandi.
  \end{itemize}
\end{resume_section}

\end{document}
```
